Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects

### 2014-09-04 android-stacks.tex
results

As mentioned before, the tool enables a set of exception stack traces analyses by combining exception stack 
trace information with bytecode and sourcecode analysis. Each analysis is implemented as a different module 
on Exception miner. The main analyses provided by the tool are presented next:

@@

\emph{\textbf{Exception Signaler Analysis.}}
This module is responsible for classifying each signaler according 
to its origin (i.e. Android Application Framework, Android Libcore, Application, Library). 
Table~\ref{tab:signalers} presents the heuristic adopted in this classification.
To enable such classification, we needed to feed this module the information
comprising all Java packages that compose: the Android Plaform;
 the Android Libcore; and each analyzed Application. 
To discover the packages composing the first two origins
we could reffer to the Android Specification.
To discover the packages composing each application, this module 
extracted the manifest files of each Android app
 - which defines the main packages that compose the applications.
 When this file was not available we recursevely analyzed the 
structure of source-code directories composing the app
- filtering out the cases on which the application 
also included the source-code of reused libraries.
Then based on this information and using pattern matching 
between the signaler name and the packages this module identifies 
the origin of the exception signalers. The exceptions were considered
 from libraries if their packages were not defined 
on Android Platform, core libraries nor on applications.
Table ~\ref{signalers} summarizes the signaler classification.

@@

%The information extracted by each module was structured in a Database,
%which contained the distilled information of stack traces, exception types,
%and signalers origin (e.g., root cause, root cause type, root cause signaler and its origin,
%exception wrappers,  types, and its signalers).

%\subsubsection{The ExceptionMiner Tool}
%Using the ExceptionMiner tool, developed in this work, we could extract the exception stack traces defined 
%on issues and issue comments. Executing ExceptionMiner tool each issue and issue comment defined on the 
%16,836 projects considered in this study, we could observe that 3,758 projects (22,32\%) contained at 
%least 1 issue on which a stack trace was found. Overall the number of issues on which a stack trace was
% found was 21,013 from which 28,800 stack traces were extracted and analyzed - some issues defined 
% more than one stack trace.

%We then analyzed the labels associated to such issues, and we discovered that only 5,196 were
% labled as defect ~\footnote{the dedect lables considered in this work were every lable containing 
%as substring: defect, bug, crash, failure, fail, exception} (which represent only 24,7\% of the
% issues on which a stack trace was found), most of the issues on which stack traces were found 
%contained no lable. Such observation supports our assumption to consider not only the issues 
% related with defect issues on this analysis.

%\begin{figure*}
%\centering
%\includegraphics[width=\hsize]{overview.pdf}
%\caption{Overview of the study based on mixed approaches.}
%\label{fig:overviewfig}
%\end{figure*}

@@

Next section presents the results for each of the study phases, providing both a
quantitative and qualitative analysis of the outcomes.

@@

%To answer this question, we mined from every extracted stack trace the top level
%exception being signaled, its signaler (the first method signature frame after
%the exception), the root exception (the exception which initiated the stack
%trace, defined on the bottom of the stack), and the root signaler. The
%intermediate elements that compose a stack trace as shown in
%Figure~\ref{fig:wrapping} (i.e., the intermediate causes and its execution
%stacks) were not be considered in the analysis.
%~\todo{Move this to the previous section? IMO, It is better to keep all facts
%about how we did the research in one place
%RSC: I WAS ABOUT TO MOOVE BUT THERE WAS ALREADY A SIMILAR TEXT ON 
%THE EXCEPTION DISTEILLER}

This section presents the results aimed at answering the research 
questions presented before.

@@

\emph{\textbf{Identifying the Concerns Related to Root Exceptions.}} To get a broader view of the root exceptions of stack traces,
 we performed an empirical evaluation whose goal was to identify the concerns related to the most reported root exceptions. 
Since it is infeasible to inspect the code responsible for throwning every exception reported in this study.
This identification performed in this study was based on meaning that the name of the exception holds, 
its description (i.e., Javadoc documentaion), and the Java specification. To exemplify, an instance of ArrayOutOfBoundException
 usually refers to a programming mistake. Moreover, the Java specification list all exceptions related to backward compatibility 
issues ~\cite{javaback} (e.g., InstantiationError, VerifyError, IllegalAccessError). Some concerns are known as sources 
of faults in mobile development are: concurrency ~\cite{ama2012} backward compatibility  
~\cite{McDon13}, security  ~\cite{enck2011study,was2010} and resource management (IO, Memory, Batery) ~\cite{Zhang12}.
However, there are exceptions that cannot be directly mapped to one of such concerns. Either because they are
related to programming mistakes - as illustrated on the previously. Or because they are too general (i.e.,  java.lang.Exception,
java.lang.RuntimeException, java.lang.Error). Or also because they are related to other concerns (e.g., specific to a given library).

>>>>

As mentioned before, the tool enables a set of exception stack traces analyses by combining exception stack 
trace information with bytecode and sourcecode analysis. Each analysis is implemented as a different module 
on Exception miner. Next, we present core analyses which were implemente on ExceptionMiner. Such analyses 
provide aditional information to be used on further analyses described in Section ~\ref{sec:result}:

@@

\emph{\textbf{Exception Signaler Analysis.}}
This module is responsible for classifying each signaler according 
to its origin (i.e. Android Application Framework, Android Libcore, Application, Library). 
Table~\ref{tab:signalers} presents the heuristic adopted in this classification.
To enable such classification, we needed to feed this module the information
comprising all Java packages that compose: the Android Plaform;
 the Android Libcore; and each analyzed Application. 
To discover the packages composing the first two origins
we could reffer to the Android Specification.
To discover the packages composing each application, this module 
extracted the manifest files of each Android app
 - which defines the main packages that compose the applications.
 Whenever this file was not available, we recursevely analyzed the 
structure of source-code directories composing the app
- filtering out the cases on which the application 
also included the source-code of reused libraries.
Then based on this information and using pattern matching 
between the signaler name and the packages this module identifies 
the origin of the exception signalers. The exceptions were considered
 from libraries if their packages were not defined 
on Android Platform, core libraries nor on applications.
Table ~\ref{signalers} summarizes the signaler classification.

@@

@@

@@

This section presents the results of the study, providing both a
quantitative and qualitative analysis of the outcomes. The structure of this section
 is centered on questions that guied the search for 
source-code fragilities based on exception stack trace information.

@@

\emph{\textbf{The prevalence of programming mistakes.}} To get a broader view of the prevalence of
programming mistakes of reported exception stack traces we performed the following analysis....

 we performed an empirical evaluation whose goal was to identify the concerns related to the most reported root exceptions. 
Since it is infeasible to inspect the code responsible for throwning every exception reported in this study.
This identification performed in this study was based on meaning that the name of the exception holds, 
its description (i.e., Javadoc documentaion), and the Java specification. To exemplify, an instance of ArrayOutOfBoundException
 usually refers to a programming mistake. Moreover, the Java specification list all exceptions related to backward compatibility 
issues ~\cite{javaback} (e.g., InstantiationError, VerifyError, IllegalAccessError). Some concerns are known as sources 
of faults in mobile development are: concurrency ~\cite{ama2012} backward compatibility  
~\cite{McDon13}, security  ~\cite{enck2011study,was2010} and resource management (IO, Memory, Batery) ~\cite{Zhang12}.
However, there are exceptions that cannot be directly mapped to one of such concerns. Either because they are
related to programming mistakes - as illustrated on the previously. Or because they are too general (i.e.,  java.lang.Exception,
java.lang.RuntimeException, java.lang.Error). Or also because they are related to other concerns (e.g., specific to a given library).
